%!TEX program = xelatex

% Presentazione finale delle tavole applicative per il corso di controllo dei robot
% Enrico Puglisi & Andrea Ryals

\input{tex/preamble}

\begin{document}
%
% Title page
\frame{\titlepage}
%
%Table of contents
\begin{frame}
\frametitle{Table of contents}
\begin{multicols}{2}
\tableofcontents
\end{multicols}
\end{frame}


%
\include{tex/delta}
%
\include{tex/ball_plate}
%
\begin{frame}[allowframebreaks]
  \frametitle<presentation>{Bibliography}
  \begin{thebibliography}{10}
  \beamertemplatearticlebibitems
  \bibitem{Clavel1991}
    R.~Clavel.
    \newblock {\em Conception d'un robot parallele rapide {\`{a}} 4 degres de libert{\'{e}}}.
    \newblock 1991.
  %
  \beamertemplatearticlebibitems
  \bibitem{Rey1999}
    L.~Rey, R.~Clavel.
    \newblock The Delta Parallel Robot.
    \newblock {\em Parallel Kinematic Machines. Advanced Manufacturing. Springer, London}, 1999.
  %
  \beamertemplatearticlebibitems
  \bibitem{Codourey1991}
    A.~Codourey.
    \newblock Contribution {\`{a}} la commande des robots rapides et pr{\'{e}}cis application au robot delta.
    \newblock 1999.
  %
  \beamertemplatearticlebibitems
  \bibitem{Edelsbrunner1983}
    H.~Edelsbrunner, D.~Kirkpatrick, R.~Seidel.
    \newblock On the Shape of a Set of Points in the Plane.
    \newblock {\em IEEE Trans. Inf. Theor.}, 1983.
  %
  \beamertemplatearticlebibitems
  \bibitem{Ho2013}
    M.~T.~Ho, Y.~Rizal, L.~M.~Chu.
    \newblock Visual servoing tracking control of a ball and plate system: Design, implementation and experimental validation.
    \newblock {\em International Journal of Advanced Robotic Systems}, 2013.
  %
  \beamertemplatearticlebibitems
  \bibitem{Ho2013}
    J.~Hauser, S.~sastry, P.~Kokotovic.
    \newblock Nonlinear Control VIa Approximate Input-Output Linearization: The Ball and Beam Example.
    \newblock {\em IEEE transaction on Automatic control}, 1992.
  \end{thebibliography}
\end{frame}
\end{document}



@misc{Hauser1992,
author = {Hauser, John and Shankar, Sastry and Kokotovic, Petar},
publisher = {IEEE transaction on Automatic control},
title = {{Nonlinear Control VIa Approximate Input-Output Linearization: The Ball and Beam Example}},
year = {1992}
}